### 2016-02-15 mcmc.tex
lam citation

A key question for an \MCMC\ operator---\emph{the} key question in some
sense---is \emph{how long to run} to be sure of having reliable
results.
It is disappointing and annoying to many that there is no extremely
simple and reliable answer to this question.

>>>>

A key question for an \MCMC\ operator---\emph{the} key question in some
sense---is \emph{how long to run} to be sure of having reliable
results.
It is disappointing and annoying to many that there is no extremely
simple and reliable answer to this question.\note{There is very good
  coverage of most of the points in this \sectionname, and more, in a
  set of lecture notes by Patrick Lam up at
  \url{http://www.people.fas.harvard.edu/~plam/teaching/methods/convergence/convergence_print.pdf}.}
